---
title: "Data transformation"
author: "Hans"
date: "4/13/2021"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup,cache=FALSE,include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r getdata}
df <- airquality
df
```

#dealing with missing values
#1:Omit
```{r omit incomplete}
df1 <- df[complete.cases(df),]

df1
```


#2:Replacing missing values with mean
```{r replace}
df$Ozone[is.na(df$Ozone)]=mean(df$Ozone,na.rm = TRUE)
df
```

```{r}
df$Solar.R[is.na(df$Solar.R)]=mean(df$Solar.R,na.rm = TRUE)
df
```


```{r}
df$Ozone=round(df$Ozone,digits = 1)
df
df$Solar.R=round(df$Solar.R,digits = 1)
df
```

**Plots**
#1:Barchart

```{r}
df3 <- head(df)
df3
```

```{r}
barplot(df3$Ozone,xlab = "count",ylab = "ozone value",col = "green",main = "OZONE BARCHART",border = "yellow")
```


#Adding legend to chart?

#code eg.
#legend("topleft",regions,cex=1.3,fill=("green","pink"))


#2:**Pie chart**

#code\n

#pie(x,labels,radius,main,col,clockwise)\n

#x-vector that contains numeric value used in pie chart\n

#labels-used to give description to slices\n

#radius-?\n

#Main-title\n

#Cot-colour of the palette\n

#clockwise-logical value that indicates the clockwise or anti-clockwise direction in which slices are drawn\n

```{r}
pie(df3$Ozone)
```
#Adding title to pie chart
```{r}
pie(df3$Ozone,main = "ozone pie chart")
```


#3:**Boxplot**
#measure of how data is distributed in a data set

#boxplot(x,data,notch,varwidth,names,main)

#x-vector or formula

#data-data frame

#Notch-logical value set as true to draw a notch

#varwidth-logical value set as true to draw width of box same as sample size.

#names-is a group of labels that will be printed under each boxplot

#main-title



#Boxplot using Notch-helps find out how medians of different data groups match with each other.

#NB:Colour not applied below

```{r}
boxplot(mpg~cyl,data = mtcars,xlab = "Quantity of Cylinders",ylab = "Miles per Gallon",notch=TRUE,varwidth=TRUE,ccol=c("yellow","blue","red"),names=c("High","Medium","Low"))
```

#4:**Line Graph**
#Is a pictorial representation of information which changes over time.

#plot(v,type,col,xlb,ylab)

#v -vector containing numeric values

#type-this parameter takes only values ?l?to draw only line or?p? to draw the points and"o" to draw both point and line

```{r}
plot(df3$Ozone,type = "o",col="green",xlab = "count",ylab = "Ozone level",main = "ozone trend line graph")
```

#5:**Scatter plot**

#used to compare variables

#each point on the scatter plot defines value of two variables

#plot(x,y,main,xlab,ylab,xlim,ylim,axes)

#x- data set whose values are on the horizontal axis

#y-?

#main-?

#xlab-label of horizontal axis

#ylab-?

#xlim-limit of x values which are used for plotting

#ylim-?

#axes-indicates if both axes should be drawn on the plot.


```{r}
data <- mtcars[,c("wt","mpg")]
data
plot(x=data$wt,y=data$mpg,xlab = "Weight",ylab = "Milage",xlim = c(2.5,5),ylim = c(15,30),main = "Weight v/s Milage",col="green")

```


#6:**histogram**

#A histogram is a type of bar chart which shows frequency of values which are compared with a set of values range.

#Histogram is used for distibution whereas  a barchart is used for comparing different entities

#hist(v,main,xlab,ylab,xlim,ylim,breaks,col,boarder)

#v-vector with numeric values.

#Break-Used to mention the width of each bar.

```{r}
v <- c(12,24,16,38,21,13,55,17,39,10,60)
v
hist(v,xlab = "weight",ylab = "frequency",col = "pink",border="yellow",main = "histogram of V")
```

#Using limits

```{r}
hist(v,xlab = "weight",ylab = "frequency",col = "blue",border="yellow",main = "histogram of V",xlim = c(0,40),ylim = c(0,3),breaks = 5)
```

#Finding return value of histogram

```{r}
m <- hist(v)
m
```
#ggplot syntax
#ggplot(data=df,aes(x=?,y=?,group=1))+geom_line(linetype="dashed")+geom_point()


