---
title: "Data transformation"
author: "Hans"
date: "4/13/2021"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
df <- airquality
df
```

#dealing with missing values
#1:Omit
```{r}
df1 <- df[complete.cases(df),]

df1
```


#2:Replacing missing values with mean
```{r}
df$Ozone[is.na(df$Ozone)]=mean(df$Ozone,na.rm = TRUE)
df
df$Ozone <- round(df$Ozone,digits = 2)
df  
```

```{r}
df$Solar.R[is.na(df$Solar.R)]=mean(df$Solar.R,na.rm = TRUE)
df$Solar.R <- round(df$Solar.R,digits = 2)
df
```


```{r}
df$Solar.R[is.na(df$Solar.R)]=mean(df$Solar.R,na.rm = TRUE)
df
```

**Plots**
#1:Barchart

```{r}
df3 <- head(df)
df3
```

```{r}
barplot(df3$Ozone,xlab = "count",ylab = "ozone value",col = "black",main = "OZONE BARCHART",border = "yellow")
```


#Adding legend to chart?

#code eg.
#legend("topleft",regions,cex=1.3,fill=("green","pink"))


**Pie chart**
#code
#pie(x,labels,radius,main,col,clockwise)
#x-vector that contains numeric value used in pie chart
#labels-used to give description to slices
#radius-?
#Main-title
#Cot-colour of the palette
#clockwise-logical value that indicates the clockwise or anti-clockwise direction in whuch slices are drawn
```{r}
pie(df3$Ozone,main="Ozone Pie")
```
#Adding title to pie chart
```{r}
pie(df3$Ozone,main = "ozone pie chart")
```

#3:**Boxplot**
#measure of how data is distributed in a data set
#boxplot(x,data,notch,varwidth,names,main)
#x-vector or formula
#data-data frame
#Notch-logical value set as true to draw a notch
#varwidth-logical value set as true to draw width of box same as sample size.
#names-is a group of labels that will be printed under each boxplot
#main-title

```{r}
mtcars
boxplot(mpg~cyl,data = mtcars,xlab = "Quantity Of Cylinders",ylab = "Miles per Gallon",main="Mtcars Boxplot")
```

#Boxplot using Notch-helps find out how medians of different data groups match with each other.

#NB:Colour not applied below

```{r}
boxplot(mpg~cyl,data = mtcars,xlab = "Quantity of Cylinders",ylab = "Miles per Gallon",notch=TRUE,varwidth=TRUE,ccol=c("yellow","blue","red"),names=c("High","Medium","Low"))
```
#3:**Line Graph**
#Is a pictorial representation of information which changes over time.
#plot(v,type,col,xlb,ylab)
#v -vector containing numeric values
#type-this parameter takes only values ?l?to draw only line or?p? to draw the points and"o" to draw both point and line
```{r}
plot(df3$Ozone,type = "o",col="green",xlab = "count",ylab = "Ozone level",main = "ozone trend line graph")
```

#4:**Scatter plot**
#used to compare variables
#each point on the scatter plot defines value of two variables

#plot(x,y,main,xlab,ylab,xlim,ylim,axes)
#x- data set whose values are on the horizontal axis
#y-?
#main-?
#xlab-label of horizontal axis
#ylab-?
#xlim-limit of x values which are used for plotting
#ylim-?
#axes-indicates if both axes should be drawn on the plot.


```{r}
data <- mtcars[,c("wt","mpg")]
data
plot(x=data$wt,y=data$mpg,xlab = "Weight",ylab = "Milage",xlim = c(2.5,5),ylim = c(15,30),main = "Weight v/s Milage",col="green")

```

