---
title: "Data Reshaping"
author: "De Farmer"
date: "4/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(comment="#>",echo = FALSE)
```

#Data Reshaping is about how data  is organised in rows and columns.

#It involves merge,split,and changing rows to column.

#1:**Transpose of a matrix**

#t(matrix/data frame)

```{r}
print("Creating matrix")

a <- matrix(c(4:12),nrow=3,byrow = TRUE)
a
print("matrix after transpose")
b <- t(a)
b
```

#Joining rows and columns in data frame

#R allows to join multiple vectors to create a data frame.Fot this purpose R provides cbind().It also provides rbind(),which allows to merge two data frames.

#cbind(vector1,vector2,...............vectorN)

#rbind(dataframe1,dataframe2..........dataframeN)

```{r}
Name <- c("Joy","Peter","Hans","Pesh")
Adress <- c("Mwingi","Matuu","Eldoret","Juja")
Marks <- c(342,332,410,390)
info <- cbind(Name,Adress,Marks)
info
```

#creating another data frame with similar columns

```{r}
info1 <- data.frame(Name=c("Liz","Kadzo"),Adress=c("Kamuwongo","Machakos"),Marks=c(287,354),stringsAsFactors = TRUE)
info1
```

#Combining both data frames

#NB:Error

```{r info,error=FALSE}
all.info <- rbind(info,info1)
all.info
```


#Merging data frame??

#melting of data and casting of molten data??


```{r}
D=read.csv("C:\\Users\\dennis\\Desktop\\kabati cycle21.csv")
D
```


#Creating user_defined functions in R
#A function is a collection of **instructions or statements** that work together to accomplish a definite task.
#Syntax ====**Function_name <- function(arguments){**
#**function_body**
#**return (return)**
#**}**
#user defined fuction to check divisibility by three using if else control structure 
```{r}
check <- function(x){
  if(x%%3==0){
    result <- "the number is divisible by three"
  }else {
    result = "the number is not divisible by three"
  }
  result
}
check(6)
check(2)
```


#User defined function to perform reciprocal of a number.
```{r}
may <- c(28,64,63,43,56,46,87,34,73)
reciprocal <- function(vec){
  vec <- 1/vec
 # rvec1 <- reciprocal(vec1)
  return(vec)
}
reciprocal(may)
```

#User defined function to perform factorial of a number

```{r}
fact=function(a){
  facto=1
# check is the number is negative, positive or zero
if(a < 0) {
print("Sorry, factorial does not exist for negative numbers")
} else if(a == 0) {
print(1)
} else {
for(i in 1:a) {
facto = facto * i
}
print(facto)
}
}
fact(0)

fact(5)
```
user defined funtion to compute mean
```{r}
soph=function(x){
  n=length(x)
  return(sum(x)/n)
}

```

