---
title: "Islr2"
author: "hansdefarmer"
date: "5/31/2022"
output:
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

ls()-look at alist of all objects saved.
rs()-removes what we dpont want.
mass-datasets and functions. 
Islr2- datasets.

**LINEAR REGRESSION**
```{r}
library(MASS)
```
```{r}
df<-Boston
attach(df)
df
```
```{r}
head(df)
mod1<-lm(medv~lstat, data = df)
mod1
summary(mod1)
```
checking other info stored in lm function.
```{r}
names(mod1)
coef(mod1)
```
confidence intervals.
```{r ,kable()}
confint(mod1)
```
```{r}
predict(mod1,data.frame(lstat=(c(5,10,15))),interval="confidence")
```
Predict ()-predict outcomes from a generated model.
```{r}
predict(mod1,data.frame(lstat=(c(5,10,15))),interval="prediction")
```
plot regresion lines.
```{r}
plot(medv,lstat)
mod1<-lm(medv~lstat, data = df)
abline(mod1)
```
There is non linearity.
```{r}
#abline(mod1,pch=20)
```

Diagonistic plots.

```{r}
par(mfrow=c(2,2))
plot(mod1)
```
rstudent()-returns studentized values.
```{r}
plot(predict(mod1),residuals(mod1))


plot(predict(mod1),rstudent(mod1))
```

**MULTIPLE REGRESSION**
  
  
```{r}
mod2=lm(medv~lstat+age,data=Boston)
mod2
summary(mod2)
```

KNN regression- tries to predict the value of the output variable by using the local average.

KNN classification- attempts to predict class to which the output variable belongs by computing the local probability

Using Auto data **regression**

```{r, kable()}
library(MASS)
dt1<-Auto
dt1
attach(dt1)
```

```{r}
atm1<-lm(mpg~horsepower,data=dt1)
summary(atm1)
#The model is significant
```

```{r}
horse<-data.frame(horsepower=98)
horse
predict(atm1,newdata=horse)
#value of mpg when horsepower is 98=24.46
# prediction of prediction.
predict(atm1,horse,interval = "prediction")
# prediction of confidence interval associated with confidence itself.
predict(atm1,horse,interval = "confidence")
```

Plot abline for the model above.
Diagonistic plot
```{r}
par(mfrow=c(2,2))
plot(atm1)
```
Scatterplot matrix
```{r}
pairs(dt1)
#scatterplot matrix for subset of data.
pairs(~mpg+horsepower+acceleration,data=dt1)
```


Multiple

```{r}
#Deleting a column of a dataframe.**1: set column to null,create a new dataframe and exclude the unwanted from original data.eg df[,-5] removing the fifth column.
dt1
cor(dt1)
```

```{r}
mt1<-lm(mpg~cylinders+displacement+horsepower+weight+acceleration+year+origin,data = dt1)
summary(mt1)
#predictors with statistically significant relationship to response =weight, yera,and origin.
```
```{r}
#diagonistic plot
par(mfrow=c(2,3))
plot(mt1)
```

carseats dataset analysis

```{r}
library(ISLR2)
Carseats
attach(Carseats)

```
```{r}
mod2<-lm(Sales~Price+Urban+US,data = Carseats)
summary(mod2)
```
Confidence interval for the model.
```{r}
moche<-lm(Sales~Price+Price+US,data = Carseats)
summary(moche)

confint(moche)
```


