---
title: "Regressin"
author: "De Farmer"
date: "4/26/2021"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**Linear Regression**

#Linear regressin is used topredict the value of an outcome variable y on the basis of one or more imput vaiables x.ie it is used toestablish linear relationship betweenresponse and predictor variable.

#y=mx+b

#Syntax 

#lm(formula,data)

#**Formula**-is the symbol that represents relation between x and y.

#**Data**-is a vector on which we will apply the formula.

**Creating Relationship model and Getting Coefficients**

```{r}
x <- c(141,134,178,156,108,116,119,143,162,130)
y <- c(62,85,56,21,47,17,76,92,62,58)
#applying lm() function
model <- lm(y~x)
model

```

```{r}
#summary of the model
summary(model)
```

**The Predict() Function**

#predict(object,newdata)

#**Object**-is the formula that we have already predicted using the lm() function

#**NewData**-is the vector that contains the new value for predictor variable.

#Finding weight for person with height 170.

```{r}
z <- data.frame(x=160)
predictr <-predict(model,z) 
predictr
```

#**plotting Regression**
```{r}
plot(y,x,col="pink",main = "weight and height regression",abline(lm(x~y)),cex=1.3,pch=16,xlab = "weight in Kgs",ylab = "height in cm")
```


**MULTIPLE LINEAR REGRESSION**

#used to predict outcome variable (y) based on multiple distinct variables.

#y=b0+b1*x1+b2*x2+b3*x3.....bnxn

#The b value represents regression weight.They measure association between outcome and predictor variable.

#**Y**-response variable.

#**b0,b1,b2,b3...,bn**-coefficients

#**x1,x2,x3,....xn**-predictor vaiables

#Syntax

#lm(y~x1+x2+x3+.....xn,data)

```{r}
data <-mtcars 
data
head(data)
```
**Creating relation model and finding coefficients**

```{r}
imput <- mtcars
```


```{r}
model1 <- lm(mpg~wt+disp+hp,data=imput)
model1
b0 <- coef(model1)[1]
b0
x_wt <- coef(model1)[2]
x_wt
x_disp <- coef(model1)[3]
x_disp
x_hp <- coef(model1)[4]
x_hp
```

```{r}
cor(imput$mpg,imput$cyl)
```

