---
title: "T test"
author: "De Farmer"
date: "6/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#**T-test**-is used to check if mean of two groups is equal to each other.
#The null hypothesis is that two means are the same,and the alternative is that they are not identical.
#T-test syntax
  **Dependent 2-group T-test**
#t.test(y~x)...where y is numeric and x is binary factor
  **Independent 2-group T-test**
#t.test(y1,y2)...where y1 and y2 are numeric variables
  **Paired T-test**
#t.test(y1,y2,paired=TRUE)...y1 and y2 are numeric
  **One sample T-test**
#t.test(y,mu=3)...here Ho:mu=3

  **HOW TO PERFORM T-test in R**
#To specify equal variance and pooled variance we set var.equal=TRUE
#we also use alternative="less" or alternative="greater" for specifying one- tailed test
```{r}
set.seed(0)
ship <- c(rnorm(70,mean = 35000,sd=2000))
ship
t.test(ship,mu=35000)
```

**Independent T-test**
#Equal variance not assumed
```{r}
set.seed(0)
df <- rnorm(50,mean=300,sd=70)
df1 <- rnorm(50,mean = 305,sd=70)
t.test(df,df1,var.equal = FALSE)
```
  **paired T-test**
```{r}
set.seed(2800)
pre <- c(rnorm(2000,mean = 130,sd=5))
post <- c(rnorm(2000,mean = 144,sd=4))

t.test(pre,post,paired = TRUE)
```

