---
title: "time series"
author: "hansdefarmer"
date: "8/23/2021"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
**R-Time series Analysis**

Any metric is measured over a regular time forms a time series.

**Time series**-Is a collection of observations made sequentially in time.
Creating a Time series-ts() function is used to create a time series

E.g timeseries<-ts(data,start,end,frequency)

**Data**-Vector or matrix which contains values used in time series
**Start**-start time for the first observation.
**End**-end time for the last observation.
**Frequency**-specifies number of observations per unit time
Example ,Consider the annual snowfall details at a place starting from January 2013.

```{r}
snowfall <- c(790,1170.8,860.1,1330.6,630.4,911.5,683.5,996.6,783.2,982,881.8,1021)
timeseries <- ts(snowfall,start = c(2013,1),frequency = 12)
timeseries
```

```{r}
library(tseries)
plot.ts(timeseries,main="Time series Plot")
```
########################################################

**Stationary Time Series**

A series is stationary if ;

1. Mean value of series is constant over time.That implies that trend component is declared null.

2.Variance should not increase over time.

3.The seasonality effect should be minimal.

i.e it is a trendseasonal pattern .which resembles a random white noise  regardless of time interval observed.

NOTE:Stationary Time Series is the one whose  statistical properties like mean ,variance ,and autocorrrelation, etc are all constant over time.
######################################################

Differencing time series data to make it stationary

**forex data AUD\JPY**
clearing allvariables in the Workspace
```{r}
rm(list = ls())
#loading the forecasting package
library(fpp2)
```
Importing the data
```{r}
jpy=read.csv("C:\\Users\\dennis\\Downloads\\AUD_JPY (1 T).csv")
jpy
jpy=jpy[,3]
jpy
#converting to time series data. Time is in seconds i.e, changes occuring in every second
jpyt=ts(jpy,start = c(7,1),frequency = 20)
```
Preliminary analysis
```{r}
#Time plot
autoplot(jpyt)+ggtitle("Change In AUD/JPY Forex.Time plot")+
  ylab("AUD/JPY")
```

Differencing the data to remove trend
```{r}
dy=diff(jpyt)
#plotting differeced data.
autoplot(dy)+ggtitle("Differenced Change in AUD/JPY :Forex Time Plot")+
  ylab("AUD/JPY")
```

Differencing the second time to make the data stationary and remove trend
```{r}
dy0=diff(dy)
#plotting differeced data.
autoplot(dy0)+ggtitle("Differenced2 Change in AUD/JPY :Forex Time Plot")+
  ylab("AUD/JPY")
```
series appear trend-stationary,use to investigate seasonality.

```{r}
ggseasonplot(dy0)+ggtitle("Seasonal Plot: Change in AUD/JPY :Forex Time Plot")+
  ylab("AUD/JPY")
```
Another seasonal plot, the subseries plot.
```{r}
ggsubseriesplot(dy0)+ggtitle("subseries Plot: Change in AUD/JPY :Forex Time Plot")+
 ylab("AUD/JPY")
#**Each season requires at least 2 observations** for doing sub series plot

```

##############################################################

If our model has seasonality and trend we take the first difference.
Forecast with various methods

##############################################################
###########
use benchmark method to forecast.
Using seasonal naive method as our benchmark
y_t = y_(t-s)+e_t

##########
```{r}
fit=snaive(dy0) #residual=0.007
summary(fit)
checkresiduals(fit)
```

#########
Fit exponential smoothing
Fit ETS method

#########
```{r}
fit_ets=ets(dy0) #residual= 0.0728011
summary(fit_ets)
checkresiduals(fit_ets)
```

#########
fitting arima model

#########
```{r}
fit_arima=auto.arima(jpyt,d=1,D=1,stepwise = FALSE,approximation = FALSE,trace = TRUE) #residual= 0.04872371
summary(fit_arima)
checkresiduals(fit_arima)
forecast(fit_arima)
```

Forecast using seasonal naive model
```{r}
fcast=forecast(fit,h=40)
summary(fcast)
autoplot(fcast,include = 80)
```



Time series data from R- airpassengers.

```{r}
ps=AirPassengers
class(ps)

```
```{r}
boxplot(ps,notch = TRUE)
```

